ActiVis: Mobile Object Detection and Active Guidance for People with Visual Impairments

### 2019-07-04 paper.tex
a few fixes and comments

@@

\author{J.C. Lock\inst{1} \and
  A.G. Tramontano\inst{2} \and
  S. Ghidoni\inst{2} \and
  N. Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{University of Lincoln, Lincoln, UK \and
  Universit\`{a} degli studi di Padova, Italy
}

@@

There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
This work is part of the ActiVis\footnote{lcas.github.io/ActiVis} project that aims to enable people with vision impairments (PwVI) to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment with a blindfolded participant. }\label{fig:system-in-use}
\end{figure}

@@

A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
$r$ in this case is the target object.

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/control_loop.png}
  \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects}\label{fig:openimage}
\end{figure}

@@

We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector.
These objects given by

\begin{equation*}
  \begin{split}
    \mathbf{U} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}.
  \end{split}
\end{equation*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment. }\label{fig:boxplot-displacement}
\end{figure}

@@

The next steps for the project are to refine and expand the object detector to include objects from other environments.

>>>>

\usepackage{soul}
\DeclareRobustCommand{\tofix}[1]{{\sethlcolor{yellow}\hl{[#1]}}}

@@

\author{J.C. Lock\inst{1} \and
  A.G. Tramontano\inst{2} \and
  S. Ghidoni\inst{2} \and
  N. Bellotto\inst{1}
}
\authorrunning{Jacobus C. Lock et. al.}
\institute{School of Computer Science, University of Lincoln, United Kingdom \and
 Department of Information Engineering, University of Padova, Italy
}

@@

There are an estimated half a billion people that live with mild to severe vision impairment or total blindness and this number is expected to significantly rise with an ageing population~\cite{bourne2017magnitude}.
There has been a rise interest from industrial partners in utilising modern technology to make their products more accessible and improvements in modern computing power and image processing capabilities have made this easier.
This work is part of the ActiVis\footnote{http://lcas.github.io/ActiVis} project that aims to enable people with vision impairments to independently navigate and find objects within an unknown indoor environment using only a mobile phone and its camera.
This system implements active vision ideas~\cite{bajcsy2017}, but replaces the electro-mechanical servo typically found in active vision systems with a user's arm and hand as pictured in Fig.~\ref{fig:system-in-use}.
This project expands upon concepts proposed in~\cite{bellotto2013,lock2017portable} and builds off of the system introduced in~\cite{lock2019active}.

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{figures/system_use.png} \hfil
  \includegraphics[width=0.45\textwidth]{figures/system_use.png}
  \caption{The system in use during an experiment with a blindfolded participant. \tofix{can you add another image with (most of) the objects? maybe arranged in a grid} }\label{fig:system-in-use}
\end{figure}

@@

A complete system diagram for Activis is given in Fig.~\ref{fig:sys-diagram}. 
This diagram shows a typical feedback control loop that generates a control signal to minimise some error signal, \emph{e}, and drive the output to some reference, $r$, but has been modified to incorporate a human within the loop.
In this case, $r$ is the target object.

\begin{figure}[t]
  \centering
  \includegraphics[width=0.7\textwidth]{figures/control_loop.png}
  \caption{The system control loop including a human and the controller.}\label{fig:sys-diagram}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png} \hfil
  \includegraphics[width=0.45\columnwidth]{figures/desk_example.png}
  \caption{An example from of an image from the OpenImage dataset~\cite{openimages} containing typical office objects. \tofix{add one more image, different from VISAPP though}}\label{fig:openimage}
\end{figure}

@@

We encoded 16 objects, including a `nothing' object where the detector does not see anything of interest, into the controller and object detector:
\begin{equation*}
  \begin{split}
    \mathbf{U} = \{ nothing, monitor, keyboard, mouse, desk, laptop, mug, window,\\ 
      lamp, backpack, chair, couch, plant, telephone, whiteboard, door \}.
  \end{split}
\end{equation*}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.7\textwidth]{figures/boxplot_time_to_target.png}
  \caption{A set of boxplots comparing the time to target for each experiment. }\label{fig:boxplot-time}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{figures/boxplot_displacement.png}
  \caption{A set of boxplots comparing the linear and angular displacement the device travelled for each experiment.\tofix{Half the height of the image. You can also put it together with Fig.~4 to save space.}}\label{fig:boxplot-displacement}
\end{figure}

@@

The next steps for the project are to refine and expand the object detector to include objects from other environments. \tofix{that's it? a little bit more imagination... what about user- adaptation? different interface, maybe with different audio, voice, vibration etc.? evaluation with larger pool of VI participants? It doesn't mean you have to do it, but it gives ideas for future improvements and research projects.}
